Easy as Pi: A Network Coding Raspberry Pi Testbed

### 2016-06-06 measurements.tex
Goodput done

In Figs.\ref{fig:enc_good_rasp2_packet_gf2} and
\ref{fig:enc_good_rasp2_packet_gf256}, we observe that the packet size for
the maximum \ac{RLNC} goodput has shifted towards 8 KiB, indicating that
the \ac{Raspi} 2 is able to handle $16 \times 8$ KiB $= 128$ KiB. This is
possible because the \ac{Raspi} 2 has a shared L2 cache of 256 KiB allowing
to still allocate some space for the data to be processed.

@@

Description

\begin{figure*}
    \centering
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=1.15\textwidth]{images/06_06_2016/goodput_vs_generation_size_Rasp_v2_decoder_Binary_1600.eps}
        \caption[]%
        {{\small Goodput vs. Generation size for $q = 2$}}
        \label{fig:dec_good_rasp2_gen_gf2}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=1.15\textwidth]{images/06_06_2016/goodput_vs_generation_size_Rasp_v2_decoder_Binary8_1600.eps}
        \caption[]%
        {{\small Goodput vs. Generation size for $q = 2^8$}}
        \label{fig:dec_good_rasp2_gen_gf256}
    \end{subfigure}
    \vskip\baselineskip
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=1.15\textwidth]{images/06_06_2016/goodput_vs_symbol_size_Rasp_v2_decoder_Binary_16.eps}
        \caption[]%
        {{\small Goodput vs. Packet size for $q = 2,\ g=16$}}
        \label{fig:dec_good_rasp2_packet_gf2}
    \end{subfigure}
    \quad
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=1.15\textwidth]{images/06_06_2016/goodput_vs_symbol_size_Rasp_v2_decoder_Binary8_16.eps}
        \caption[]%
        {{\small Goodput vs. Packet size for $q = 2^8,\ g=16$}}
        \label{fig:dec_good_rasp2_packet_gf256}
    \end{subfigure}
    \caption[]
    {\small Decoder goodput measurements for the \ac{Raspi} 2}
    \label{fig:dec_good_rasp2}
\end{figure*}

Description

\subsection{Average Power}
With the energy measurement setup described in Section \ref{sec:energy_metrics_methods},
we compute the metrics described there. We first proceed with the average
power consumption of the \ac{Raspi} 1 in Fig. \ref{fig:current_rasp1} and
the \ac{Raspi} 2 in Fig. \ref{fig:current_rasp2}.

\begin{figure*}
    \centering
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=1.15\textwidth]{images/06_06_2016/current_vs_sec_raspberry_change_gen_from_-10sec_to_500sec.eps}
        \caption[]%
        {{\small Current for the \ac{Raspi} 1}}
        \label{fig:current_rasp1}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=1.15\textwidth]{images/06_06_2016/current_vs_sec_raspberry2_change_gen_from_-10sec_to_500sec.eps}
        \caption[]%
        {{\small Current for the \ac{Raspi} 2}}
        \label{fig:current_rasp2}
    \end{subfigure}

>>>>

In Figs.\ref{fig:enc_good_rasp2_packet_gf2} and
\ref{fig:enc_good_rasp2_packet_gf256}, we observe that the packet size for
the maximum \ac{RLNC} goodput has shifted towards 8 KiB, indicating that
the \ac{Raspi} 2 is able to handle $16 \times 8$ KiB $= 128$ KiB. This is
possible because the \ac{Raspi} 2 has a shared L2 cache of 256 KiB allowing
to still allocate some space for the data to be processed while achieving
a maximum goodputs of 105 MB/s.

@@

In Figs.~\ref{fig:dec_good_rasp1} and \ref{fig:dec_good_rasp2}, we
observe the same generation and packet size effects reported in the
encoding case. However, we do observe in
Figs.~\ref{fig:dec_good_rasp1_gen_gf2}, \ref{fig:dec_good_rasp1_gen_gf256},
\ref{fig:dec_good_rasp2_gen_gf2} and \ref{fig:dec_good_rasp2_gen_gf256};
that duplicating the generation size does not reduce by a factor of 4 the
goodput. In principle, given that Gaussian elimination scales as
$\mathcal{O}(g^3)$ (and thus the processing time), we would expect that
the goodput scales as $\mathcal{O}(R_{proc,dec}) = \mathcal{O}(g/g^{3}) =
\mathcal{O}(g^{-2})$. This would imply that duplicating the generation
size, should reduce the goodput by a factor of 4, which does not. Instead,
the goodput it is only reduced by a factor of 2. This is only possible if
the Gaussian elimination is $\mathcal{O}(g^2)$. A study in
\textbf{[refence about Achutan's measurements on the Raspi]} indicated
that this is effectively the case. The reason is that the $g^2$ factor in
the scaling law for our Gaussian elimination is much higher than the $g^3$
for $g \geq 512$. \textbf{[Why was the $g^2$ factor greather than the
$g^3$ factor? Wasn't it due to the amount of of bytes per packet?]}

Another difference with the encoding goodput results in the same figures,
is that even though the \ac{TSNC} with $e = 16$ packets provides the fastest
encoding, it does not happen to be the same for the decoding. For this
very sparse scheme, the decoding is affected by the amount of \ac{l.d.}
packets generated by, which leads to a higher delay in some cases
(particularly in $g = [64,\ 128]$). For other generation sizes, the
performance of sparse codes is similar.
%
\begin{figure*}
    \centering
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=1.15\textwidth]{images/06_06_2016/goodput_vs_generation_size_Rasp_v2_decoder_Binary_1600.eps}
        \caption[]%
        {{\small Goodput vs. Generation size for $q = 2$}}
        \label{fig:dec_good_rasp2_gen_gf2}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=1.15\textwidth]{images/06_06_2016/goodput_vs_generation_size_Rasp_v2_decoder_Binary8_1600.eps}
        \caption[]%
        {{\small Goodput vs. Generation size for $q = 2^8$}}
        \label{fig:dec_good_rasp2_gen_gf256}
    \end{subfigure}
    \vskip\baselineskip
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=1.15\textwidth]{images/06_06_2016/goodput_vs_symbol_size_Rasp_v2_decoder_Binary_16.eps}
        \caption[]%
        {{\small Goodput vs. Packet size for $q = 2,\ g=16$}}
        \label{fig:dec_good_rasp2_packet_gf2}
    \end{subfigure}
    \quad
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=1.15\textwidth]{images/06_06_2016/goodput_vs_symbol_size_Rasp_v2_decoder_Binary8_16.eps}
        \caption[]%
        {{\small Goodput vs. Packet size for $q = 2^8,\ g=16$}}
        \label{fig:dec_good_rasp2_packet_gf256}
    \end{subfigure}
    \caption[]
    {\small Decoder goodput measurements for the \ac{Raspi} 2}
    \label{fig:dec_good_rasp2}
\end{figure*}
%
\subsection{Average Power}
With the energy measurement setup described in Section
\ref{sec:energy_metrics_methods}, we compute the metrics described there.
We first proceed with the average power consumption of the \ac{Raspi} 1
in Fig.~\ref{fig:current_rasp1} and the \ac{Raspi} 2 in
Fig.~\ref{fig:current_rasp2}.

\begin{figure*}
    \centering
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=1.15\textwidth]{images/06_06_2016/current_vs_sec_raspberry_change_gen_from_-10sec_to_500sec.eps}
        \caption[]%
        {{\small Current for the \ac{Raspi} 1 model}}
        \label{fig:current_rasp1}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=1.15\textwidth]{images/06_06_2016/current_vs_sec_raspberry2_change_gen_from_-10sec_to_500sec.eps}
        \caption[]%
        {{\small Current for the \ac{Raspi} 2 model}}
        \label{fig:current_rasp2}
    \end{subfigure}
